%!TEX root = ../../main.tex

\subsection{Relevant Weather Information} \label{sec:relevantweatherinformation}

One of the criteria according to the initial problem statement (sec. \ref{sec:ips}) is the definition of the weather conditions where it is relevant to apply sonification.


\subsubsection{Pre-test} \label{sec:pretest} 

An early test was conducted in order to identify and define the relevant weather information. 
The test took the form of a simple interview including open ended questions.
The questions were designed to identify the situations in which the users consult a weather forecast and what specific information they are looking for when looking at a weather forecast.
The provided situations will be used in a delimitation to find a suitable situation where sonification of weather information may provide an improvement or an equal experience to visually represented weather information.
The important weather features provided will be used to identify what conditions should be sonified as the audio should only provide information that the user will actually find relevant.
\bigskip

Because the test has no target group other than people who have at some point checked a weather forecast, the test will be conducted using random sampling (XX). 
Random sampling selects every subject in the test from a greater group of subjects (the target group) completely at random.
Every subject has an equal chance to get picked to do the survey.
\bigskip

The following questions are defined in order to specify what relevant information, as described in the initial problem statement, is. 
We are able to assume that relevant information is any information which is somehow related to weather conditions, but as every aspect might not be as relevant as some other to the individual, we therefore ask the target group the following questions in order to obtain knowledge of what specific weather data is the most prominent and important to that specific person.

The questions are formulated as:

\begin{itemize}
\item Have you within the past month checked the weather forecast once or several times?
\end{itemize}
As mentioned above, the target group for this survey is any member of the general population that has at some point in the past month checked a weather forecast.
This question is asked to make sure that this is in fact the case.

\begin{itemize}
\item Mention what/ which specific situations you find it most useful to you, to check the weather forecast?
\end{itemize}

An important aspect of a weather forecast is the purpose of obtaining the knowledge. 
This question will give an indication of some or several situations where the action of gathering information about the weather is of greatest importance to the individual.

\begin{itemize}
\item Based upon the above mentioned situation(s), what are the most important weather conditions that you find relevant in that scenario?
\end{itemize}

As we want to define a specific list/ amount of weather data which is of most relevance to the target group, we ask for specific weather conditions that they find of most importance when looking at a weather forecast.


The complete survey and answers to the survey can be found in appendix (XX).
\bigskip

\begin{table}[!htbp]
    \centering
    \begin{tabular}{ l | r }
        \textbf{Category} & \textbf{Occurrences}\\
        \hline
        Transportation Related: & \\
        * Going somewhere in the morning & 5 \\
        * General non-specified transportation & 4 \\
        Event related activities: & \\
        * Outside activities & 12 \\
        * Morning/evening. No activity is specified & 7 \\
        * Travel & 2 \\
        General/ other & 4 \\
    \end{tabular}
    \caption{Categorized answers} \label{tab:categorizedAnswers}
\end{table}

Table \ref{tab:categorizedAnswers} indicates that the majority of the sampled population find it most relevant to check the weather forecast before engaging in outside activities as well as checking the forecast as the start of the day.

\begin{table}[!htbp]
    \centering
    \begin{tabular}{ l | r }
        \textbf{Weather condition} & \textbf{Occurrences} \\
        \hline
        Temperature & 14 \\
        Downpour & 23 \\
        Wind/ Wind speed & 13 \\
        Wind direction & 1 \\
        Sunshine/ cloudy \& misc. & 6 \\
    \end{tabular}
    \caption{Weather condition answers} \label{tab:weatherConditions}
\end{table}

Table \ref{tab:weatherConditions} shows what weather conditions the sampled population find the most important/ relevant when looking at the weather forecast on-demand.
The table indicates that most subjects look primarily for the temperature, wind conditions and downpour.
\bigskip

The pre-test indicates that people look at the weather forecast at the start of their day and before engaging in outside activities.
The test also indicate that when people look at the weather forecast, they look for temperature, wind and downpour related information.
Because only relevant weather conditions should be sonified, this data will show what weather conditions are relevant to focus the sonification at as well as under which situations the sonification can be utilized.
