\section{Evaluation} \label{sec:evaluation}


\subsection{Introduction}
The evaluation will be divided into three separate test scenarios. As we are looking into how we can convey weather data through sonification, and how intuitively understood this information compared to visual representations of similar data is, it will be possible to evaluate upon by isolating and comparing data from several tests, where one test is of the produced sonifications, another test with visual elements and one test where both visuals and sonifications is tested. 


More specifically described, a test will be conducted solely where the weather sonifications are presented to test subjects. Similar, a test will be conducted where the visual representations will be presented with the same procedure as the sonification, and finally a test where both visual representations along with the sonification of the data. 
This procedure will make it possible to compare what the test subjects can deduct from the presented data, and allow us to make comparisons towards what information the visual, sonification and combined representations of data is conveying, and thereby make it possible to evaluate upon how well the sonification formulate weather data.

\subsection{Method: Evaluation}
The primary reason of the evaluation is to establish knowledge as to determine if the list of requirements has been fulfilled and to make it possible to gain satisfying results which helps answering to the final problem statement.

The implemented product contains sonifications of specific weather categories, where theese categories has been further categorised into sonifications of different values which represent low, medium and high values of a specific weather category.



\subsection{Hypothesis}

Describe Null and alternative hypothesis.

\subsection{test procedure}

describe the test procedure and course of the test.

\subsection{Test results}

\subsection{Test Evaluation}


